Selective electroporation of the viral envelope

### 2021-05-17 documents/pure_electroporation.tex
Musings on detection in wastewater

\usepackage[left=2cm,right=2cm,
top=0.85cm,
bottom=1.5cm,%
headheight=11pt,%
letterpaper]{geometry}

@@

@@

\begin{abstract}
	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores in, and perhaps the destruction of, membranes; this is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown to be safe and effective in the clinic for the in-situ ablation of tumors.

@@

@@

In a continued effort to make ultracrepidarian physicists such as ourselves feel useful

While both mechanisms hinge on a set of time constants, those discussed in the previous paper referred to the time for viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging, and Smoluchowski processes. Previously, the relevant quantities describing damage to the virion were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.

@@

hit "with an electric field strong enough to knock over a horse, and they do enough things to justify international meetings, to fill a sizable book, and to lead one to speak of an entirely new technology for cell manipulation."

@@

These regimes of intensity may possibly be accessible via ultrashort optical techniques. Similarly, Tsen \cite{Studies2014} report a non-electroporative mechanism, but these results have not been successfully independently replicated at that intensity\cite{No2011}.

on the other hand, the idea of shocking a virus is so basic that it can scarcely be believed

@@

@@

The concept of optimizing an electroporation pulse is not novel, having been discussed by many groups in the past; either to prodduce different sterilization effects, tee Retelj use a series of

>>>>

\usepackage[left=2cm,right=2cm,
top=1.25cm,
bottom=1.5cm,%
headheight=11pt,%
letterpaper]{geometry}

@@

 \pagestyle{empty}

@@

\begin{abstract}
	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores in, and perhaps the destruction of, membranes; this is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown clinically to be safe and effective for the in-situ ablation of tumors.

@@

%send to jeff on the discord?

@@

In a continued effort to make ultracrepidarian pseudo-physicists such as ourselves feel useful

\begin{tcolorbox}
While both mechanisms hinge on a set of time constants, those discussed in the previous paper referred to the time for viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging, and Smoluchowski processes. Previously, the relevant quantities describing damage to the virion were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter. 
\end{tcolorbox}

@@

when a strong electric field is applied, they "do enough things to justify international meetings, to fill a sizable book, and to lead one to speak of an entirely new technology for cell manipulation."

@@

These regimes of intensity may possibly be accessible via ultrashort optical techniques. Accordingly, Tsen \cite{Studies2014} report a non-electroporative mechanism, but these results have not been successfully independently replicated at that intensity\cite{No2011}.

@@

Also be of some use for testing and detection.

@@

The concept of optimizing an electroporation pulse is not novel, having been discussed by many groups in the past; either to prodduce different sterilization effects, tee Retelj use a series of, to
